Microxanox - an R package for simulating an \(MICR\)obial ecosystem that can occupy \(OX\)ic or \(ANOX\)ic states.

### 2022-05-03 inst/manuscript/manuscript_microxanox.tex
Add compiled manuscript

\documentclass[]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%
\usepackage[hyphens]{url}

@@

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\usepackage{graphicx}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Microxanox - an R package for simulating an MICRobial ecosystem that can occupy OXic or ANOXic states.},
            colorlinks=true,
            urlcolor=blue,
            linkcolor=blue,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

% Pandoc syntax highlighting
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}

@@

% Pandoc citation processing
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
% for Pandoc 2.8 to 2.10.1
\newenvironment{cslreferences}%
  {}%
  {\par}
% For Pandoc 2.11+
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

  \title{Microxanox - an R package for simulating an \(MICR\)obial
ecosystem that can occupy \(OX\)ic or \(ANOX\)ic states.}
    \author[University of Zürich]{Rainer M Krug\corref{Corresponding
Author}}
   \ead{Rainer.Krug@uzh.ch \& Rainer@krugs.de} 
    \author[University of Zürich]{Owen L. Petchey}
   \ead{Owen.Petchey@ieu.uzh.ch} 
      \address[University of Zürich]{Department of Evolutionary Biology
and Environmental Studies, Winterthurerstrasse 190, 8057 Zurich}
      \cortext[1]{Corresponding Author}
    \cortext[2]{Equal contribution}

  \begin{abstract}
  Ca. 100 words.
  \end{abstract}
   \begin{keyword} metadata quality; data curation; archival; long term
storage; R package;\end{keyword}
 \end{frontmatter}

@@

Many ecosystems are exposed to gradual changes of environmental
variables, to which the responses are not always as gradual as the
change of the environmental variable. One example where the gradual
change of a single environmental causing an abrupt change of the system
is the switch from an aerobic to anaerobic system. This system hass been
investigated by Bush et al. (\protect\hyperlink{ref-Bush2017}{2017}). We
wanted to take this investigation one step further, and look at the role
of an increased biodiversity plays in these dynamics
(\protect\hyperlink{ref-REF_NEEDED}{REF NEEDED, 2222}). For this
purpose, we developed this package.

The microxanox package is a package for simulating a three functional
group system (\emph{CB}: cyanobacteria, \emph{PB}: phototrophic sulfur
bacteria, and \emph{SB}: sulfate-reducing bacteria) with four chemical
substrates (\emph{P}: phosphorus, \emph{O}: oxygen, \emph{SR}: reduced
sulfur, \emph{SO}: oxidized sulfur). It includes feddback between
biogeochemical processes and is based on
(\protect\hyperlink{ref-Bush2017}{Bush et al., 2017}) (See
(\protect\hyperlink{ref-Bush2017}{Bush et al., 2017}) for a detailed
discussion of the model).

The aims of the \texttt{microxanox} package are twofold. Firstly, the
package aims at reproducing the results shown by
(\protect\hyperlink{ref-Bush2017}{Bush et al., 2017}), which is
acomplished in the \href{LINK\%20NEEDED}{vignette Partial reproduction
of Bush et al}. Secondly, to take these results one step further, it
includes new functionality to adress our research question as presented
in (\protect\hyperlink{ref-REF_NEEDED}{REF NEEDED, 2222}).

@@

In addition to the model itself, the package includes some functions to
analyse the results as well as visualise the results to provide a
starting point for customised visualisations based on own requirements.

@@

\{\textgreater\textgreater Describe the software in as much as is
necessary to establish a vocabulary needed to explain its
impact.\textless\textless\}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{@startuml}
\NormalTok{partition "Run Single Simulation" \{}
\NormalTok{   start}
\NormalTok{  :parameter \textless{}{-} new\_runsim\_parameter();}
\NormalTok{  split}
\NormalTok{    \#palegreen:saveRDS(FILE, parameter);}
\NormalTok{    detach}
\NormalTok{  split again}
\NormalTok{    \#pink:result \textless{}{-} run\_simulation(parameter);}
\NormalTok{  end split}
\NormalTok{  split}
\NormalTok{    \#palegreen:saveRDS(FILE, results);}
\NormalTok{    detach}
\NormalTok{  split again}
\NormalTok{    :Change some parameter;}
\NormalTok{    \#pink:result2 \textless{}{-} run\_simulation(results);}
\NormalTok{  end split}
\NormalTok{  split}
\NormalTok{    \#palegreen:saveRDS(FILE, results2);}
\NormalTok{    detach}
\NormalTok{  split again}
\NormalTok{    end}
\NormalTok{  end split}
\NormalTok{\}}
\NormalTok{@enduml}
\end{Highlighting}
\end{Shaded}

\includegraphics{/var/folders/50/wcr5bjwn75q595n6x82gxj280000gq/T//RtmpRw3cq4/runsim_example.pdf}

The package is not intended to provide a modelling framework which can
be adjusted easily to all needs, but primarily a tool to implement the
model used by (\protect\hyperlink{ref-Bush2017}{Bush et al., 2017}) and
to extend it to our needs (\protect\hyperlink{ref-REF_NEEDED}{REF
NEEDED, 2222}). Consequently, any more substantial changes and
adaptaitions, are likely to need a change in the source code.

Nevertheless, the model is structured in a way which builds on a modular
structuere, so that e.g.~the event definition can easily be changed. or
other aspects can be adjusted. All values in the parameter object can be
changed as needed and the general structure of the code should make it
not to difficult to adapt the model to other similar systems.

@@

\{\textgreater\textgreater Give a short overview of the overall software
architecture; provide a pic- torial component overview or similar (if
possible). If necessary provide im- plementation
details.\textless\textless\}

The framework used when writing this package aims at reproducibility of
the results. It builds on the folowing main considerations:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  all parameter needed to run a simulation or find a stable state are
  contained in a single parameter object. This object is created by
  using the functions \texttt{new\_...\_parameter()},
  \texttt{new\_initial\_state()} and \texttt{new\_strain\_parameter()}.
  Which one of the \texttt{new\_...\_parameter()} functions has to be
  used when, will be discussed in the section @ref(runsim) and in the
  \href{LINK_NEEDED}{User Guide}.
\item
  The function call \texttt{run\_...(parameter)} will run the simulation
  using the parameter as defined in the object \texttt{parameter}.
\item
  The return value of the \texttt{run\_...(parameter)} function is
  identical to the parameter object plus an additionl slot named
  \texttt{results} which contains the results of the run
\item
  As this return value contains all parameter, it is possible to re-run
  the simulatuion by simply running \texttt{run\_...(result)}.
\end{enumerate}

@@

A typical simulation would look as followed:

\begin{Shaded}
\begin{Highlighting}[]
\DocumentationTok{\#\# Create the parameter}
\NormalTok{parameter }\OtherTok{\textless{}{-}} \FunctionTok{new\_runsim\_parameter}\NormalTok{()}
\CommentTok{\# manually setting certain parameter}

\DocumentationTok{\#\# Run the simulation and save the result}
\NormalTok{result }\OtherTok{\textless{}{-}} \FunctionTok{run\_simulation}\NormalTok{(parameter)}
\FunctionTok{saveRDS}\NormalTok{(result, }\StringTok{"sim1.rds"}\NormalTok{)}

\DocumentationTok{\#\# Do other stuff, e.g. plotting}

\DocumentationTok{\#\# Load results, change some parameter, and rerun the simulation and save the result}
\NormalTok{parameter }\OtherTok{\textless{}{-}} \FunctionTok{loadRDS}\NormalTok{(}\StringTok{"sim1.rds"}\NormalTok{)}
\CommentTok{\# change some parameter}
\NormalTok{result }\OtherTok{\textless{}{-}} \FunctionTok{run\_simulation}\NormalTok{(parameter)}
\FunctionTok{saveRDS}\NormalTok{(result, }\StringTok{"sim2,rds"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\hypertarget{software-functionalities}{%
\subsection{Software Functionalities}\label{software-functionalities}}

\{\textgreater\textgreater Present the major functionalities of the
software.\textless\textless\}

We will now discuss the general structure and functionality of the
package without going into to much detail. A more detailed discussion
can be found in the \href{LINK_NEEDED}{User Guide}.

The ODEs for the rates of change are specified in the function
\texttt{bushplus\_dynamic\_model()}. This augmented version of the model
published in (\protect\hyperlink{ref-Bush2017}{Bush et al., 2017}) can
handle multiple strains within each of the three functional groups,
temporal variation in oxygen diffusivity, and events.

@@

\hypertarget{illustrative-examples}{%
\section{Illustrative Examples}\label{illustrative-examples}}

\{\textgreater\textgreater Present the major functionalities of the
software.\textless\textless\}

@@

The individual simulation (\texttt{run\_simulation()} function) is the
working horse in this package. In this function, the ODEs are solved.
The function needs only one argument - an object as created by the
function \texttt{new\_runsim\_parameter()}. One parameter of this object
is the \texttt{strain\_parameter} which can be created by the function
\texttt{new\_strain\_parameter()}. For a detailed description of the
parameter and how they are created please see the User Guide and which
acomnpanies the package or is available at \href{@LINK_NEEDED}{User
Guide}

@@

The function \texttt{plot\_dynamics()} plots a single simulation run, as
returned from the \texttt{run\_simulation()} function. This functio is
only provided as a convenience function to provide a way to easily see
the results of a simulation run. An example plot resulting from this
function is shown in @ref(fig:plot-dynamics).

@@

{\centering \includegraphics[width=500px]{figures/ug_three_strains_dynamics}

@@

This is implemented in the function \texttt{run\_temporal\_ssfind()},
which takes a parameter object as created by the function
\texttt{new\_temporal\_ssfind\_parameter()} and a number indicating the
.

@@

\{\textgreater\textgreater This is the main section of the article and
the reviewers weight the description here appropriately Indicate in what
way new research questions can be pursued as a result of the software
(if any). Indicate in what way, and to what extent, the pursuit of
existing research questions is improved (if so). Indicate in what way
the software has changed the daily practice of its users (if so).
Indicate how widespread the use of the software is within and outside
the intended user group. Indicate in what way the software is used in
commercial settings and/or how it led to the creation of spin-off
companies (if so).\textless\textless\}

The first two use cases are described in detail in the User Guide and
the Partial Reproduction Vignettes. The third is taken from the REF
NEEDED (\protect\hyperlink{ref-REF_NEEDED}{2222}) for which this R
package was designed. All of these use cases can be expanded to larger
numbers of strains per functional group and variable values van be
changed.

\hypertarget{regime-shifts-during-temporal-environmental-change}{%
\subsection{Regime shifts during temporal environmental
change}\label{regime-shifts-during-temporal-environmental-change}}

@@

{\centering \includegraphics[width=500px]{figures/ug_three_strains_stable_state}

@@

\hypertarget{the-extent-of-hysteresis-depends-on-community-composition}{%
\subsection{The extent of hysteresis depends on community
composition}\label{the-extent-of-hysteresis-depends-on-community-composition}}

One of the reasons to develop this package was to reproduce the results
presented in Bush et al. (\protect\hyperlink{ref-Bush2017}{2017}), this
was achieved as demonstrated in the \href{LINK_NEEDED}{Partial
Reproduction supplement}. All aspects in the paper could be reproduced
and are shown in the vignette.

@@

{\centering \includegraphics[width=500px]{figures/user_guide_hysteresis}

@@

\hypertarget{effects-of-functional-diversity-on-regime-shifts}{%
\subsection{Effects of functional diversity on regime
shifts}\label{effects-of-functional-diversity-on-regime-shifts}}

As discussed in the paper (\protect\hyperlink{ref-REF_NEEDED}{REF
NEEDED, 2222}), the role biodiversity plays in abrupt regime shifts
based on gradual changing environmental parameter is not well
understood. This model (as part of the package) has been used to
investigate these dynamics and the results are available in REF NEEDED
(\protect\hyperlink{ref-REF_NEEDED}{2222}).

@@

@@

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Bush2017}{}}%
Bush, T., Diao, M., Allen, R.J., Sinnige, R., Muyzer, G., Huisman, J.,
2017. Oxic-anoxic regime shifts mediated by feedbacks between
biogeochemical processes and microbial community dynamics. Nature
Communications 8, 789.
doi:\href{https://doi.org/10.1038/s41467-017-00912-x}{10.1038/s41467-017-00912-x}

\leavevmode\vadjust pre{\hypertarget{ref-REF_NEEDED}{}}%
REF NEEDED, A., 2222. {REFERNECE NEEDED}. Journal of missing references.

\end{CSLReferences}

>>>>

\documentclass[]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%

\usepackage[hyphens]{url}

@@

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage[]{natbib}
\bibliographystyle{plainnat}

\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Microxanox - an R package for simulating an MICRobial ecosystem that can occupy OXic or ANOXic states.},
            colorlinks=true,
            urlcolor=blue,
            linkcolor=blue,
            pdfborder={0 0 0}}

@@

@@

@@

  \title{Microxanox - an R package for simulating an \(MICR\)obial
ecosystem that can occupy \(OX\)ic or \(ANOX\)ic states.}
    \author[University of Zürich]{Rainer M Krug%
  %
  \fnref{Corresponding Author}}
   \ead{Rainer.Krug@uzh.ch; Rainer@krugs.de} 
    \author[University of Zürich]{Owen L. Petchey}
   \ead{Owen.Petchey@ieu.uzh.ch} 
      \affiliation[University of Zürich]{Department of Evolutionary
Biology and Environmental Studies, Winterthurerstrasse 190, 8057 Zurich}
    \cortext[cor1]{Corresponding author}
    \fntext[1]{Corresponding Author}
    \fntext[2]{Equal contribution}

  \begin{abstract}
  Ca. 100 words.
  \end{abstract}
    \begin{keyword}
    metadata quality; data curation; archival; long term storage; R
package; \sep 
    metadata quality; data curation; archival; long term storage; R
package;
  \end{keyword}

 \end{frontmatter}

\hypertarget{todo}{%
\section{\texorpdfstring{\color{red}TODO}{TODO}}\label{todo}}

\begin{itemize}
\tightlist
\item
  \color{red}\textbf{update links}
\item
  \color{red}\textbf{update cross references} \pagebreak
\end{itemize}

@@

Many ecosystems are exposed to gradual changes of environmental
variables, to which the responses are not always as gradual as the
change of the environmental variable. One example where the gradual
change of a single environmental variable is causing an abrupt change of
the system is the switch from an aerobic to anaerobic system. This
system has been investigated by \citet{Bush2017}. We wanted to take this
investigation one step further, and look at the role an increased
biodiversity plays in these dynamics \citep{REF_NEEDED}. For this
purpose, we developed this package.

The microxanox package is a package for simulating a three functional
group system (\emph{CB}: cyanobacteria, \emph{PB}: phototrophic sulfur
bacteria, and \emph{SB}: sulfate-reducing bacteria) with four chemical
substrates (\emph{P}: phosphorus, \emph{O}: oxygen, \emph{SR}: reduced
sulfur, \emph{SO}: oxidized sulfur). It includes feedback between
biogeochemical processes and is based on \citep{Bush2017} (See
\citep{Bush2017} for a detailed discussion of the model).

The aims of the \texttt{microxanox} package are twofold. Firstly, the
package aims at reproducing the results shown by \citep{Bush2017}, which
is accomplished in the \href{LINK\%20NEEDED}{vignette Partial
reproduction of Bush et al}. Secondly, to take these results one step
further, it includes new functionality to address our research question
as published in \citep{REF_NEEDED}.

@@

In addition to the model itself, the package includes some functions to
analyse the results as well as visualize the results to provide a
starting point for customized visualizations based on own requirements.

@@

\begin{quote}
\{\textgreater\textgreater Describe the software in as much as is
necessary to establish a vocabulary needed to explain its
impact.\textless\textless\}
\end{quote}

We will discuss the general structure and functionality of the package
here without going into to much detail. A more detailed discussion can
be found in the \href{LINK_NEEDED}{User Guide}.

The model by \citet{Bush2017} is based on ODEs for the rates of change
which are specified in the function \texttt{bushplus\_dynamic\_model()}.
This augmented version of the model published in \citep{Bush2017} can
handle multiple strains within each of the three functional groups,
temporal variation in oxygen diffusivity, and events.

The package is not intended to provide a modelling framework which can
be adjusted easily to all needs, but primarily a tool to implement the
model used by \citep{Bush2017} and to extend it to our needs
\citep{REF_NEEDED}. Consequently, any more substantial changes and
adaptations are likely to need a change in the source code.

Nevertheless, the source code is structured in modular, so that e.g.~the
event definition can easily be changed, or other aspects can be
adjusted. All values in the parameter object can be changed as needed
and the general structure of the code should make it not to difficult to
adapt the model to other similar systems.

@@

\begin{quote}
\{\textgreater\textgreater Give a short overview of the overall software
architecture; provide a pictorial component overview or similar (if
possible). If necessary provide im- plementation
details.\textless\textless\}
\end{quote}

The framework used when writing this package aims at reproducibility of
the results. It builds on the following main considerations:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  all parameter needed to run a simulation or find a stable state are
  contained in a single parameter object. This object is created by
  using the functions \texttt{new\_...\_parameter()},
  \texttt{new\_initial\_state()} and \texttt{new\_strain\_parameter()}.
  Which one of the \texttt{new\_...\_parameter()} functions has to be
  used when, will be discussed in the section @ref(runsim) and in more
  detail in the \href{LINK_NEEDED}{User Guide}.
\item
  The function call \texttt{run\_...(parameter)} will run the simulation
  using the parameter as defined in the object \texttt{parameter}.
\item
  The return value of the \texttt{run\_...(parameter)} function is
  identical to the parameter object plus an additional slot named
  \texttt{results} which contains the results of the run
\item
  As the return value contains all parameter, it is possible to re-run
  the simulation by simply running \texttt{run\_...(result)}.
\end{enumerate}

@@

@@

@@

A typical simulation would look as shown in @ref(fig:runsim\_example).

\begin{verbatim}
#> [1] "./figures/simflow.pdf"
\end{verbatim}

{\centering \includegraphics[width=350px]{./figures/simflow}

\caption{Typical flow of a simulation. Dark Grey boxes: commands necessary for simulation; Light Grey:Saving of parameter and results; Lightest Grey: Different non specified commands.}\label{fig:runsim_example}
\end{figure}

The individual simulation (\texttt{run\_simulation()} function) is the
working horse in this package. In this function, the ODEs are solved.
The function needs only one argument - an object as created by the
function \texttt{new\_runsim\_parameter()}. One parameter of this object
is the \texttt{strain\_parameter} which can be created by the function
\texttt{new\_strain\_parameter()}. For a detailed description of the
parameter, their meaning and how they are created please see the User
Guide which accompanies the package or is available at
\href{@LINK_NEEDED}{User Guide}

@@

The function \texttt{plot\_dynamics()} plots a single simulation run, as
returned from the \texttt{run\_simulation()} function. This function is
only provided as a convenience function to provide a way to easily see
the results of a simulation run. An example plot resulting from this
function is shown in @ref(fig:plot-dynamics).

@@

{\centering \includegraphics[width=350px]{figures/ug_three_strains_dynamics}

@@

This is implemented in the function \texttt{run\_temporal\_ssfind()},
which takes a parameter object as created by the function
\texttt{new\_temporal\_ssfind\_parameter()}.

@@

\hypertarget{use-cases}{%
\subsection{Use Cases}\label{use-cases}}

We will now show two use cases which illustrate applications of the
package. All use cases can be used as starting points for other
investigations of the behavior of the system.

The first two use cases are described in detail in the User Guide and
the Partial Reproduction Vignettes. The third is taken from
\citet{REF_NEEDED} for which this R package was designed. All of these
use cases can be expanded to larger numbers of strains per functional
group and variable values van be changed.

\hypertarget{regime-shifts-during-temporal-environmental-change}{%
\subsubsection{Regime shifts during temporal environmental
change}\label{regime-shifts-during-temporal-environmental-change}}

@@

{\centering \includegraphics[width=350px]{figures/ug_three_strains_stable_state}

@@

We saved all parameter and result objects, so that all results are
completely reproducible. The general flow of the experiment is identical
to the one shown in @ref(fig:runsim\_example).

\hypertarget{the-extent-of-hysteresis-depends-on-community-composition}{%
\subsubsection{The extent of hysteresis depends on community
composition}\label{the-extent-of-hysteresis-depends-on-community-composition}}

One of the reasons to develop this package was to reproduce the results
presented in \citet{Bush2017}. This was achieved as demonstrated in the
\href{LINK_NEEDED}{Partial Reproduction supplement}. All aspects in the
paper could be reproduced and are shown in the vignette.

@@

{\centering \includegraphics[width=350px]{figures/user_guide_hysteresis}

@@

Ass all objects were saved, results can be easily reproduced and
parameter can be changed to assess the impact of these changes (e.g.~to
conduc a sensitivity analysis).

\hypertarget{effects-of-functional-diversity-on-regime-shifts}{%
\subsubsection{Effects of functional diversity on regime
shifts}\label{effects-of-functional-diversity-on-regime-shifts}}

As discussed in the paper \citep{REF_NEEDED}, the role biodiversity
plays in abrupt regime shifts based on gradual changing environmental
parameter is not well understood. This model (as part of the package)
has been used to investigate these dynamics and the results are
available in \citet{REF_NEEDED}.

@@

\begin{quote}
\{\textgreater\textgreater This is the main section of the article and
the reviewers weight the description here appropriately Indicate in what
way new research questions can be pursued as a result of the software
(if any). Indicate in what way, and to what extent, the pursuit of
existing research questions is improved (if so). Indicate in what way
the software has changed the daily practice of its users (if so).
Indicate how widespread the use of the software is within and outside
the intended user group. Indicate in what way the software is used in
commercial settings and/or how it led to the creation of spin-off
companies (if so).\textless\textless\}
\end{quote}

The free and open source implementation and extension of the model used
in \citet{Bush2017} provides the means of reproducing the results
published while at the same time provides the means of doing
investigations which extend the original publication, as done in
\citet{REF_NEEDED}.

The combination of all parameter in a single parameter object as well as
the return of the simulation as a result object which inherits from the
parameter object and adds a results slot provides a relatively easy to
use framework to implement reproducible experiments.

@@

\renewcommand\refname{References}
\bibliography{bibliography.bib}
